Psychological Needs During Intergroup Contact

### 2022-01-05 Methods-and-Results.Rmd
mdl tbl resize

mdlTblTheoreticalLong <- mdlTblLong %>%
  replace(is.na(.), "") %>%
  #mutate_all(linebreak) %>%
  kbl(
    .,
    caption = "Theoretical Test: Core Need Fulfillment and Allport's Conditions",
    format = "latex",
    linesep = "",
    booktabs = T,
    align = c("l", rep("c", ncol(.)-1)),
    escape = FALSE
  ) %>%
  kable_classic() %>%
  add_header_above(., c(" ", "Quality" = 2, "Attitude" = 6)) %>%
  pack_rows("Study 1: Needs", 1, 4) %>%
  pack_rows("Study 2: Needs", 5, 8) %>%
  pack_rows("Study 3: Needs", 9, 12) %>%
  pack_rows("Study 3: Allport", 13, 16) %>%
  pack_rows("Study 3: Needs & Allport", 17, 20)  %>%
  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
  save_kable("Tables/mdlTheorylong.tex")
```

>>>>

mdlTblTheoreticalLong <- mdlTblLong %>%
  replace(is.na(.), "") %>%
  #mutate_all(linebreak) %>%
  kbl(
    .,
    caption = "Theoretical Test: Core Need Fulfillment and Allport's Conditions",
    format = "latex",
    linesep = "",
    booktabs = T,
    align = c("l", rep("c", ncol(.)-1)),
    escape = FALSE
  ) %>%
  kable_classic() %>%
  add_header_above(., c(" ", "Quality" = 2, "Attitude" = 6)) %>%
  pack_rows("Study 1: Needs", 1, 4) %>%
  pack_rows("Study 2: Needs", 5, 8) %>%
  pack_rows("Study 3: Needs", 9, 12) %>%
  pack_rows("Study 3: Allport", 13, 16) %>%
  pack_rows("Study 3: Needs & Allport", 17, 20)  %>%
  kable_styling(latex_options = "scale_down") %>%
  kableExtra::landscape() %>%
  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
  save_kable("Tables/mdlTheorylong.tex")
```
